TODO

### 2022-12-09 code/annotation_analysis.Rmd
more models

@@

##  Within end-stuff

>>>>

```{r, eval=F}
to_end_same_flower <- to_end |> 
  filter(ref1==ref2) |> 
  mutate(same_player=ifelse(player1==player2,1,0),
         flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, same_player, gameId, flower)

m_to_end_sameflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_same_flower) |> write_rds(here(model_path,"m5.rds"))

show_summary_rstan(m_to_end_sameflower) |> write_rds(here(model_path,"to_end_sameflower_model.rds"))

@@

```{r, eval=F}
to_end_diff_flower <- to_end |> 
  filter(ref1!=ref2) |> 
  mutate(same_player=ifelse(player1==player2,1,0)) |> 
  select(sim, condition, earlier, same_player, gameId)

m_to_end_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_diff_flower) |> write_rds(here(model_path,"m5.rds"))

show_summary_rstan(m_to_end_diffflower) |> write_rds(here(model_path,"to_end_diffflower_model.rds"))

```
##  Within end-stuff

### 2022-12-09 write-ups/cogsci23_paper/manuscript.Rmd
more models

stats_text  <- function(model, row){
  str_c( model[row,2], " (CrI=", model[row,3],")")
}
```

@@

# TODOs
redraft intro & add citations
add figs
learn stan and run models
redraft methods
write analysis
write discussion
abstract & front matter

@@

```{r during, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Amount of words produced in referring expressions across trial in games in both conditions. A: Total words of referring language per game per trial. B: Words in each reference expression by trial. C: Total number of reference expressions per game per trial.", fig.height=6, fig.width=7}
flower_all|> 
  filter(later-earlier<3) |> 
  mutate(distance=case_when(
    player1==player2 ~ "Same person",
    game1==game2 ~ "same game",
    T ~ "different game"),
    same_flower=ifelse(ref1==ref2, "Same flower", "diff flower")
  ) |> 
ggplot( aes(x=later,y=sim,color=condition))+     
  stat_summary(aes(group=str_c(color,condition), color=condition),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.3, geom="point")+
  geom_smooth(formula=y~poly(x,2))+facet_grid(same_flower~distance)+theme(legend.position="bottom", legend.title=element_blank())+
        scale_x_continuous(limits=c(1,24), breaks=c(6,12,18,24))+
        scale_color_brewer(palette="Dark2")

@@

#wi_g_bet_f <- read_rds(here(model_path,"samegame_diffflower_model.rds"))

#bet_g_wi_f <- read_rds(here(model_path,"diffgame_sameflower_model.rds"))
```

### Within games
TODO we compare games within 2 rounds of each other (ex. trial 10 compared to 8, 9, 10, 11, 12)

@@

same person 
condition
interactions w/ trial

@@

## End expressions

>>>>

stats_text  <- function(model, row){
  str_c( model[row,2], " CrI=", model[row,3],"")
}
```

@@

# TODOs
redraft intro & add citations
add figs
consider rerunning wi_game bet flower with a mixed effect (was being slow, so didn't) and other models

redraft methods
write analysis
write discussion
abstract & front matter

@@

```{r during, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Cosine similarities between SBERT embeddings of utterances produced within 2 trials of each other. Utterances were paired with other utterances from different games; from the same game, but a different utterer speaker; or from the same speaker (vertical panels). Utterances were either in reference to different flowers or both in reference to the same flower (horizontal panels).", fig.height=4, fig.width=10, out.width="100%"}
flower_all|> 
  filter(later-earlier<3) |> 
  mutate(distance=case_when(
    player1==player2 ~ "Same Person",
    game1==game2 ~ "Same Game",
    T ~ "Different Games"),
    same_flower=ifelse(ref1==ref2, "Same Flower", "Different Flowers")
  ) |> 
ggplot( aes(x=later,y=sim,color=condition))+     
  stat_summary(aes(group=str_c(color,condition), color=condition),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.3, geom="point")+
  geom_smooth(formula=y~poly(x,2))+facet_grid(same_flower~distance)+theme(legend.position="bottom", legend.title=element_blank())+
        scale_x_continuous(limits=c(1,24), breaks=c(6,12,18,24))+
        scale_color_brewer(palette="Dark2")+
  labs(x="Trial Number", y="Cosine Similarity")+
  guides(color = guide_legend(override.aes = list(linetype = NA, alpha=1, fill=NA, size=5) ) )

@@

wi_g_bet_f <- read_rds(here(model_path,"samegame_diffflower_model.rds"))

bet_g_wi_f <- read_rds(here(model_path,"diffgame_sameflower_model.rds"))
```

### Within games

TODO we compare games within 2 rounds of each other (ex. trial 10 compared to 8, 9, 10, 11, 12)

@@

Different flowers within the same game have diverging descriptions that get less similar over time (trial: `r stats_text(wi_g_bet_f,6)`). Terms are overall slightly less similar in Shared Utility groups (`r stats_text(wi_g_bet_f,2)`), but this does not interact with trial (`r stats_text(wi_g_bet_f,3)`). There is not an effect of being said by the same person (`r stats_text(wi_g_bet_f,8)`), or interactions between who said it and trial number (`r stats_text(wi_g_bet_f,7)`) or condition (`r stats_text(wi_g_bet_f,5)`).

@@

Utterances describing the same flower in different games diverged slightly (trial: `r stats_text(bet_g_wi_f,4)`). There was a condition difference with shared utility conditions having more similar descriptions across games (`r stats_text(bet_g_wi_f,2)`); this did not interact with trial (`r stats_text(bet_g_wi_f,3)`).

TODO: what is our possibly explanation for this?!

This may be a fluke, as there are not a huge number of games in either condition, but if it's robust, it could be that the shared utility framing leads to less idiosyncratic descriptions and instead towards more universal priors. 
TODO this should be hedged *a lot* but we can also cite the study about large groupy things and the crab-like images 
```{r }

# by trial
to_end <- M_mat %>% 
  filter(seen %in% c("game", "own")) |> 
  group_by(gameId,color,condition) %>% 
  mutate(combinedId=str_c(referent,"_", trialNum, "_",seen,"_",playerId)) %>% 
  make_across_df(F_mat, 'cosine') %>% 
  separate(dim1, c("ref1", "trialNum1","seen1","player1"), convert=T) |> 
  separate(dim2, c("ref2", "trialNum2", "seen2", "player2"), convert=T) |> 
 # rename(referent1=dim1,referent2=dim2) %>% 
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  filter(seen1!=seen2) %>% 
  mutate(earlier=ifelse(trialNum1>trialNum2,trialNum2, trialNum1) |> as.numeric(),
         later=ifelse(trialNum1>trialNum2, trialNum1,trialNum2) |> as.numeric()) |> 
  ungroup()
```

```{r toend, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Cosine similarities between SBERT embeddings of utterances produced during a game and the post-game descriptions of the flowers.", fig.height=4, fig.width=6, out.width="50%"}
to_end|> 
  mutate(distance=case_when(
    player1==player2 ~ "Same Person",
    T ~ "Same Game - Different Person"),
        same_flower=ifelse(ref1==ref2, "Same flower", "Different flower")
) |> 
ggplot( aes(x=earlier,y=sim,color=condition))+     
  stat_summary(aes(group=str_c(color,condition), color=condition),fun.data = "mean_cl_boot", position = position_dodge(width=.3), alpha=.3, geom="point")+
  geom_smooth(formula=y~poly(x,2))+facet_grid(same_flower~distance)+theme(legend.position="bottom", legend.title=element_blank())+
        scale_x_continuous(limits=c(1,24), breaks=c(6,12,18,24))+
        scale_color_brewer(palette="Dark2")+
  guides(color = guide_legend(override.aes = list(linetype = NA, alpha=1, fill=NA, size=5) ) )

```{r}
to_e_wi_f <- read_rds(here(model_path,"to_end_sameflower_model.rds"))

to_e_bet_f <- read_rds(here(model_path,"to_end_diffflower_model.rds"))
```
## End expressions

### game to end
As a complementary way of looking at how referring expressions change over time as conventions are formed, we can take the post-game flower descriptions (each player was asked to provide what they would call each flower to their teammates) as the conventions.

Descriptions become more similar to the conventions over time  (trial: `r stats_text(to_e_wi_f,6)`). Utterances were more similar to the convention given by the same person (versu from a groupmate) (`r stats_text(to_e_wi_f,8)`), although this did not interact with trial number (`r stats_text(to_e_wi_f,7)`). Games in the shared utilities condition had utterances that were more similar to their conventions (`r stats_text(to_e_wi_f,2)`), but this did not interact with trial number (`r stats_text(to_e_wi_f,3)`) and did not significantly interact with same participant versus different participant (`r stats_text(to_e_wi_f,5)`).

There was not a significant divergence from the conventions for other flowers over time (trial: `r stats_text(to_e_bet_f,6)`). Terms are overall slightly less similar in Shared Utility groups (`r stats_text(to_e_bet_f,2)`), but this does not interact with trial (`r stats_text(to_e_bet_f,3)`). There is not an effect of being said by the same person (`r stats_text(to_e_bet_f,8)`), or interactions between who said it and trial number (`r stats_text(to_e_bet_f,7)`). Similarity to a different convention was slightly higher if was said by the same person in a Shared Utility group (`r stats_text(to_e_bet_f,5)`).

### within end
want to look for more similar with a group than between groups

do we want to look at the "other" (flower not in game) at all? No?
